Objective-First Nanophotonic Design Plan

### 2012-11-23 plan/plan.tex
Started on global optimization submodule.

\input ../defs.tex
\newcommand{\T}{^\dagger}
\newcommand{\reals}{{\mbox{\bf R}}}
\newcommand{\comps}{{\mbox{\bf C}}}

@@

\section{Structure of our software}
In reality, our software package consists of various modules
    which are designed to be maximally orthogonal.
The various modules are illustrated in \fig{structure}.

@@

\chapter{Theory}
\section{Mathematically rigorous statement of the problem}
As previously stated, the problem we want to solve is 
    \EE {rigorous problem statement}
        {\minimize&  \sum_i^N f_i(x_i) + g(z) \\
        \subto&     A_i(z)x_i - b_i(z) = 0,\quad\text{for $i = 1, \ldots, N.$}}
To now be more precise,
    \BI $x_i \in \comps^m$ are the field variables,
    \I  $z \in \reals^n$ is the structure variable,
    \I  $f_i(x_i) \in \comps^m \to \reals$ are the field design objectives,
    \I  $g(z) \in \reals^n \to \reals$ is the structure design objective,
    \I  $A_i(z)x_i - b_i(z)$ are the physics residuals, with
    \I  $A_i(z) \in \comps^{m \times m}$ and
    \I  $b_i(z) \in \comps^m$. \EI

@@

\subsection{Bi-affine property of the physics residual}
Critically, \eq{wave equation in E} is not only linear in $E$,
    but is also affine in $\epsilon$.
This allows us to form the extremely useful relationship,
    \E  {bi-affine property}
        {A_i(z)x_i - b_i(z) = B_i(x_i)z - d_i(x_i) = 0,}
    where $B(x_i) \in \comps^{n \times n}$ and $d(x_i) \in \comps^n$.
   % TODO: Show what B_i and d_i are explicitly.

@@

\subsection{The global optimization paradigm}

@@

\end{document}

>>>>

\input ../defs.tex

@@

\section{Structure of our software}
Our software package consists of various modules
    which are designed to be maximally orthogonal.
The various modules are illustrated in \fig{structure}.

@@

\chapter{Theory}
\section{Mathematically rigorous statement of the problem}
As previously stated, the problem we want to solve is 
    \EE {rigorous problem statement}
        {\minimize&  \sum_i^N f_i(x_i) + g(z) \\
        \subto&     A_i(z)x_i - b_i(z) = 0,\quad\text{for $i = 1, \ldots, N.$}}
To now be more precise,
    \BI $x_i \in \comps^n$ are the field variables,
    \I  $z \in \reals^n$ is the structure variable,
    \I  $f_i(x_i) \in \comps^n \to \reals$ are the field design objectives,
    \I  $g(z) \in \reals^n \to \reals$ is the structure design objective,
    \I  $A_i(z)x_i - b_i(z)$ are the physics residuals, with
    \I  $A_i(z) \in \comps^{n \times n}$ and
    \I  $b_i(z) \in \comps^n$. \EI

@@

\subsection{Bi-affine property of the physics residual}
Critically, \eq{wave equation in E} is not only linear in $E$,
    but is also affine in $\epsilon$.
This allows us to form the extremely useful relationship,
    \E  {bi-affine property}
        {A_i(z)x_i - b_i(z) = B_i(x_i)z - d_i(x_i) = 0,}
    where $B(x_i) \in \comps^{n \times n}$, $d(x_i) \in \comps^n$ and
    \BI $-\omega^2 E \to B_i(x_i)$, 
    \I  $\curl \mu^{-1} \curl E \to d_i(x_i)$. \EI

@@

\subsection{The global optimization paradigm}
In contrast to the local paradigm, 
    the global optimization paradigm utilizes an objective-first strategy
    in the design process.
Although such a strategy is not technically global,
    it is differentiated from local strategies because
    it strictly enforces all design objectives,
    even at the expense of non-zero physics residuals.

The optimization paradigm utilizes 
    the alternating directions method of multipliers\cite{ADMM} (ADMM) optimization technique, 
    which casts \eq{rigorous problem statement} in terms of the following augmented Lagrangians, 
    \E{}{\Lag(x, z, y) = \sum_i^N f_i(x_i) + 
            \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z)}^2 
            +\real\left[y_i^\cT (A_i(z)x_i-b_i(z))\right] + g(z),}
    where $\rho$ is a constant scalar and 
    $y_i$ are dual variables.

ADMM obtains the solutions for $x$ and $z$ via
    \EE{}{  x_i &\gets \argmin_{x_i} \Lag(x, z, y), \quad i = 1,\ldots,N \\
            z &\gets \argmin_{z} \Lag(x, z, y), \\
            y_i &\gets y_i + \rho (A_i(x_i) z - b(x_i)), \quad i = 1,\ldots,N.}

To obtain the correct $Q(z)$ which should be passed to the structure submodule,
    we use \eq{bi-affine property} to write
    \E{}{\argmin_z \Lag = \argmin_z g(z) 
            + \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i)}^2 
            + \real\left[ y_i^\cT ( B_i(x_i) z - d_i(x_i))\right]}
    which means that
    \E{}{Q(z) = \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i)}^2 
            + \real\left[ y_i^\cT ( B_i(x_i) z - d_i(x_i))\right].}

\subsubsection{Computation of $\argmin_{x_i} \Lag$}
Updating $x_i$, which is left to the paradigm submodule,
    involves solving $\argmin_{x_i} \Lag(x, z, y)$ for all $i = 1, \ldots, N$.
This can be accomplished via
    \E{}{\grad_{x_i}\Lag = \grad_{x_i} f_i(x_i) + }

@@

\begin{thebibliography}{99}
\bibitem{ADMM} Boyd group ADMM paper
\end{thebibliography}
\end{document}
